\section{Theory}




\subsection[Origin of the HI-Line]{Origin of the \ce{H_I}-Line}

\subsection{Angular resolution of the SRT}\label{sec:ang_res}
Using the equation relating the effective area $A_e$ and the wavelength $\lambda$ \cite[p. 149]{wilson}
\begin{equation}
    A_e \Omega_A = \lambda^2
\end{equation}
and the definitions of the effective area and the geometric area \cite[p. 148]{wilson}
\begin{equation}
    A_e = \eta A_g \qquad A_g = \pi \left( \frac{d}{2} \right) \label{eq:A_e}
\end{equation}
we can then solve for the effective antenna area.
\begin{equation}
    \Omega_A = \frac{\lambda^2}{A_g \eta} \label{eq:Omega_A}
\end{equation}
We only need to relate a solid-angle $\Omega$ to an angular resolution $\theta$ now. We define $\theta$ to be the half-angle that spans the solid-angle $\Omega$ on the unit sphere and thus arrive at the following expression.
\begin{align}
    \Omega = \int_{0}^{2\pi} d\phi \int_{0}^{\theta} d\vartheta \sin(\vartheta) \notag \\
    \Omega = 4 \pi \sin^2 \left( \frac{\theta}{2} \right) \approx \pi \theta^2 \label{eq:solid_angle}
\end{align}
By solving \eqref{eq:solid_angle} for $\theta$ and inserting \eqref{eq:Omega_A} and \eqref{eq:A_e} we get the final result.
\begin{equation}
    \theta_A = \sqrt{\frac{\Omega_A}{\pi}} = \sqrt{\frac{\lambda^2}{\frac{1}{4} \pi d^2 \eta \pi}} = \frac{2\lambda}{\pi d \sqrt{\eta}} \label{eq:half_angle}
\end{equation}

To compute the angular resolution we need the diameter of the SRT which is $d = \SI{4}{m}$ \cite[p. 4]{srt}, and the antenna efficiency which is $\eta = 0.5$ \cite[p. 2]{srt}.
Unfortunately we cannot reasonably estimate an error for the antenna efficiency $\eta$, we suspect however that the error of the antenna efficiency dominates here.
Therefore we will waive a proper error discussion here.

It is important to note that this angle is the half of the equivalent beam width, not the full width at half maximum, but this value will become useful in subsection \ref{sec:temp}.

To compute an approximation of the FWHM we can approximate the aperture as gaussian \cite[p. 2]{script} and note the following properties.
\begin{equation}
    \Omega_A \approx \int_{4\pi } d\Omega\, \exp{\left( -\frac{\theta^2}{2\sigma^2} \right)} \approx 4\pi \int_0^{\infty} d\theta \, \theta \exp{\left( -\frac{\theta^2}{2\sigma^2} \right)} = 4\pi \sigma^2
    \label{eq:gauss_integral}
\end{equation}
\begin{equation}
    \exp{\left( -\frac{(\theta_{FWHM}/2)^2}{2\sigma^2}\right)} = \frac{1}{2} \quad \implies \quad \theta_{\text{FWHM}} = 2 \sqrt{2\ln{2}} \sigma \label{eq:FWHM}
\end{equation}
using equations \eqref{eq:half_angle} - \eqref{eq:FWHM} we can then solve for $\theta_{\text{FWHM}}$
\begin{equation}
    \theta_{\text{FWHM}} = \sqrt{2\ln{2}} \, \theta_A
\end{equation}

We can then obtain the values shown in table \ref{tab:ang_res}.
\begin{table}[h]
    \centering
    \begin{tabular}{rrrr}
        \toprule
        $\theta_{\text{FWHM}}$ & Angular resolution $\theta$ & Wavelength $\lambda$ & Frequency\\
        \midrule
        \SI{3.206}{\degree} &\SI{2.723}{\degree} & \SI{21.11}{cm} & \SI{1.420}{\giga \hertz}\\
        \SI{0.455}{\degree} &\SI{0.387}{\degree} & \SI{0.30}{cm} & \SI{10.000}{\giga \hertz}\\
        \bottomrule
    \end{tabular}
    \caption{Angular resolution of the SRT at different frequencies}
    \label{tab:ang_res}
\end{table}
\subsection{Antenna, brightness and noise temperature}

\subsection{Temperature conversion}

\subsection{Expected temperature of the sun}\label{sec:temp}
If we assume that the sun is a black body near the wavelength of \SI{1.42}{\giga\hertz} we expect it to have a brightness temperature of $T_{\odot} = \SI{5778}{\kelvin}$ \cite[p. 211]{ftb}.
We have to consider however, that the half-angle size of the sun with a value of \SI{16}{\arcminute} \cite[p. 211]{ftb} is less than the angular resolution we computed in table \ref{tab:ang_res}.
Because the power measured by the telescope and the brightness temperature have a linear relationship knowing the beam filling factor $B$ will suffice.
\begin{equation}
    B = \frac{\Omega_{\odot}}{\Omega_A} = \frac{\theta_{\odot}^2}{\theta_A^2} = \SI{0.96
    }{\percent}
\end{equation}
We know that the sky itself will also contribute a temperature of $T_{\text{sky}} = \SI{2.7}{\kelvin}$ \cite[p. 4]{script}, thus we obtain the final result.
\begin{equation}
    T_{\text{measured}} = B T_{\odot} (1-B) T_{\text{sky}} = \SI{58}{\kelvin}
\end{equation}
This result is given without error due to the same reasons as in section \ref{sec:ang_res}


\subsection{Influence of elevation angle}

\subsection{Doppler shift}